Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-18 analysis/study2.qmd
updated scales and pool_coef function

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample13)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)

@@

pool_coef <- function(with = "Age", component = "Demographic", name = with, unequalrange=FALSE) {
  rez <- data.frame()
  for(intero in vars_intero) {
    data <- data.frame() 
    for(dataset in list(df1a, df1b, df2, df3, df4, 
                     df5, df6, df7a, df7b, df7c, 
                     df8a, df8b, df9, df10, df11, 
                     df12, df14, df15)) {
      if (with %in% names(dataset)) {
        d <- dataset[c(with, intero, "Sample")]
        data <- rbind(data, d)
      }
    }

@@

data <- rbind(
  data,
  pool_coef(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

@@

data <- rbind(
  data,
  make_rez(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
  make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  make_rez(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-5)"),
  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
)
```

@@

```{r}
data <- rbind(
  data,
  make_rez(with = "BPD", component="Mood", name = "Boderline Personality")
)
```

```{r}
data <- rbind(
  data,
  make_rez(with = "PID5_Antagonism", component="Maladaptive", name = "Antagonism"),
  make_rez(with = "PID5_Detachment", component="Maladaptive", name = "Detachment"), 
  make_rez(with = "PID5_Disinhibition", component="Maladaptive", name = "Disinhibition"),
  make_rez(with = "PID5_NegativeAffect", component="Maladaptive", name = "Negative Affect"),
  make_rez(with = "PID5_Psychoticism", component="Maladaptive", name = "Psychoticism")
)
```

```{r}
data <- rbind(
  data,
  make_rez(with = "SPQ_ConstrictedAffect", component="Schizotypic", name = "Constricted Affect"),
  make_rez(with = "SPQ_Eccentric", component="Schizotypic", name = "Eccentric"),
  make_rez(with = "SPQ_MagicalThinking", component="Schizotypic", name = "Magical Thinking"),
  make_rez(with = "SPQ_NoCloseFriends", component="Schizotypic", name = "No Close Friends"),
  make_rez(with = "SPQ_OddSpeech", component="Schizotypic", name = "Odd Speech"),
  make_rez(with = "SPQ_Reference", component="Schizotypic", name = "Reference"),
  make_rez(with = "SPQ_SocialAnxiety", component="Schizotypic", name = "Social Anxiety"),
  make_rez(with = "SPQ_Suspiciousness", component="Schizotypic", name = "Suspiciousness"),
  make_rez(with = "SPQ_UnusualPerceptions", component="Schizotypic", name = "Unusual Perceptions")
)
```

```{r}
#  names(select(df10, starts_with("ASQ")))
data <- rbind(
  data,
  make_rez(with = "ASQ_Imagination", component="Autistic", name = "Imagination"),
  make_rez(with = "ASQ_LackSocialSkills", component="Autistic", name = "Lack of Social Skills"), 
  make_rez(with = "ASQ_LowAttentionalSwitching", component="Autistic", name = "Low Attentional Switching"),
  make_rez(with = "ASQ_Patterns", component="Autistic", name = "Patterns and Numbers"),
  make_rez(with = "ASQ_Routine", component="Autistic", name = "Routines")
)
```

@@

data <- rbind(
  data,
  make_rez(with = "NEO_FFI_SUMSCORE", component = "Personality", name = "Neuroticism"),
  make_rez(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
  make_rez(with = "BFI_CONSCIENTIOUSNESS", component="Personality", name = "Conscientiousness"), 
  make_rez(with = "BFI_NEUROTICISM", component="Personality", name = "Neuroticism"),
  make_rez(with = "BFI_OPENNESS", component="Personality", name = "Openness"),
  make_rez(with = "BFI_EXTROVERSION", component="Personality", name = "Extraversion"),
  make_rez(with = "IPIP6_Agreeableness", component="Personality", name = "Agreeableness"),
  make_rez(with = "IPIP6_Conscientiousness", component="Personality", name = "Conscientiousness"), 
  make_rez(with = "IPIP6_Neuroticism", component="Personality", name = "Neuroticism"),
  make_rez(with = "IPIP6_Openness", component="Personality", name = "Openness"),
  make_rez(with = "IPIP6_Extraversion", component="Personality", name = "Extraversion"), 
  make_rez(with = "IPIP6_HonestyHumility", component="Personality", name = "Honesty-Humility")
)
```

@@

data <- rbind(data, make_rez(with = "PI_Alive", component="World Beliefs", name = "Alive"))

@@

```{r}
data <- rbind(
  data,
  make_rez(with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs", name = "Extraterrestrial"),
  make_rez(with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs", name = "Global Conspiracies"),
  make_rez(with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs", name  = "Government Malfeasance"),
  make_rez(with = "GCBS_InformationControl", component="Conspiracy Beliefs", name = "Information Control"),
  make_rez(with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs", name = "Personal Wellbeing")
)
```

```{r}
data <- rbind(
  data,
  make_rez(with = "LIE_Ability", component="Lying Profile", name = "Ability"),
  make_rez(with = "LIE_Frequency", component="Lying Profile", name = "Frequency"),
  make_rez(with = "LIE_Contextuality", component="Lying Profile", name = "Contextuality"),
  make_rez(with = "LIE_Negativity", component="Lying Profile", name = "Negativity")
)
```

@@

```{r}
# names(df1a)
# names(df1b)
# names(df2)  #TAS, MAIA, ICQ, BPQ, BVAQ
# names(df3)  # TAS, BPQ
# names(df4)  # BPQ, PBCS (private bodily consciousness?), MAIA, BAQ, BRS
# names(df5)  
# names(df6)  # PHQ2, GAD2, SSS8, IATS
# names(df7a)  # STAIT, MAIA, CES (not reported in the paper), FFMQ, NEOFFI
# names(df7b)  # BPQ, PHQ15, PHQ9, MAIA, STAIT, 
# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ 
# names(df8a)  # EDI, BPQ
# names(df8b)  # PHQ9, PHQ15, TAS
# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
# names(df10)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
# names(df11)  # PHQ4, STAIT5, BDI, MAIA
# names(df12) # MAIA, PI, 
# names(df14) # MAIA, TAS, MFQ(DEP), STAI(ANX)
# names(df15)

>>>>

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample13)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)
df16 <- cbind(data$df16, scores$sample16)

@@

pool_coef <- function(with = "Age", component = "Demographic", name = with, unequalrange=FALSE) {
  rez <- data.frame()
  for(intero in vars_intero) {
    data <- data.frame() 
    for(dataset in list(df1a, df1b, df2, df3, df4, 
                     df5, df6, df7a, df7b, df7c, 
                     df8a, df8b, df9, df10, df11, 
                     df12, df14, df15, df16)) {
      if (with %in% names(dataset)) {
        d <- dataset[c(with, intero, "Sample")]
        data <- rbind(data, d)
      }
    }

@@

data <- rbind(
  data,
  pool_coef(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)",unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
  pool_coef(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  pool_coef(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-5)"),
  pool_coef(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
)
```

@@

```{r}
data <- rbind(
  data,
  pool_coef(with = "BPD", component="Mood", name = "Boderline Personality")
)
```

```{r}
data <- rbind(
  data,
  pool_coef(with = "PID5_Antagonism", component="Maladaptive", name = "Antagonism"),
  pool_coef(with = "PID5_Detachment", component="Maladaptive", name = "Detachment"), 
  pool_coef(with = "PID5_Disinhibition", component="Maladaptive", name = "Disinhibition"),
  pool_coef(with = "PID5_NegativeAffect", component="Maladaptive", name = "Negative Affect"),
  pool_coef(with = "PID5_Psychoticism", component="Maladaptive", name = "Psychoticism")
)
```

```{r}
data <- rbind(
  data,
  pool_coef(with = "SPQ_ConstrictedAffect", component="Schizotypic", name = "Constricted Affect"),
  pool_coef(with = "SPQ_Eccentric", component="Schizotypic", name = "Eccentric"),
  pool_coef(with = "SPQ_MagicalThinking", component="Schizotypic", name = "Magical Thinking"),
  pool_coef(with = "SPQ_NoCloseFriends", component="Schizotypic", name = "No Close Friends"),
  pool_coef(with = "SPQ_OddSpeech", component="Schizotypic", name = "Odd Speech"),
  pool_coef(with = "SPQ_Reference", component="Schizotypic", name = "Reference"),
  pool_coef(with = "SPQ_SocialAnxiety", component="Schizotypic", name = "Social Anxiety"),
  pool_coef(with = "SPQ_Suspiciousness", component="Schizotypic", name = "Suspiciousness"),
  pool_coef(with = "SPQ_UnusualPerceptions", component="Schizotypic", name = "Unusual Perceptions")
)
```

```{r}
#  names(select(df10, starts_with("ASQ")))
data <- rbind(
  data,
  pool_coef(with = "ASQ_Imagination", component="Autistic", name = "Imagination"),
  pool_coef(with = "ASQ_LackSocialSkills", component="Autistic", name = "Lack of Social Skills"), 
  pool_coef(with = "ASQ_LowAttentionalSwitching", component="Autistic", name = "Low Attentional Switching"),
  pool_coef(with = "ASQ_Patterns", component="Autistic", name = "Patterns and Numbers"),
  pool_coef(with = "ASQ_Routine", component="Autistic", name = "Routines")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "NEO_FFI_SUMSCORE", component = "Personality", name = "Neuroticism"),
  pool_coef(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
  pool_coef(with = "BFI_CONSCIENTIOUSNESS", component="Personality", name = "Conscientiousness"), 
  pool_coef(with = "BFI_NEUROTICISM", component="Personality", name = "Neuroticism"),
  pool_coef(with = "BFI_OPENNESS", component="Personality", name = "Openness"),
  pool_coef(with = "BFI_EXTROVERSION", component="Personality", name = "Extraversion"),
  pool_coef(with = "IPIP6_Agreeableness", component="Personality", name = "Agreeableness"),
  pool_coef(with = "IPIP6_Conscientiousness", component="Personality", name = "Conscientiousness"), 
  pool_coef(with = "IPIP6_Neuroticism", component="Personality", name = "Neuroticism"),
  pool_coef(with = "IPIP6_Openness", component="Personality", name = "Openness"),
  pool_coef(with = "IPIP6_Extraversion", component="Personality", name = "Extraversion"), 
  pool_coef(with = "IPIP6_HonestyHumility", component="Personality", name = "Honesty-Humility")
)
```

@@

data <- rbind(data, pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"))

@@

```{r}
data <- rbind(
  data,
  pool_coef(with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs", name = "Extraterrestrial"),
  pool_coef(with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs", name = "Global Conspiracies"),
  pool_coef(with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs", name  = "Government Malfeasance"),
  pool_coef(with = "GCBS_InformationControl", component="Conspiracy Beliefs", name = "Information Control"),
  pool_coef(with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs", name = "Personal Wellbeing")
)
```

```{r}
data <- rbind(
  data,
  pool_coef(with = "LIE_Ability", component="Lying Profile", name = "Ability"),
  pool_coef(with = "LIE_Frequency", component="Lying Profile", name = "Frequency"),
  pool_coef(with = "LIE_Contextuality", component="Lying Profile", name = "Contextuality"),
  pool_coef(with = "LIE_Negativity", component="Lying Profile", name = "Negativity")
)
```

@@

```{r}
# names(df1a)
# names(df1b)
# names(df2)  #TAS, MAIA, ICQ, BPQ, BVAQ
# names(df3)  # TAS, BPQ
# names(df4)  # BPQ, PBCS (private bodily consciousness?), MAIA, BAQ, BRS
# names(df5)  
# names(df6)  # PHQ2, GAD2, SSS8, IATS
# names(df7a)  # STAIT, MAIA, CES (not reported in the paper), FFMQ, NEOFFI
# names(df7b)  # BPQ, PHQ15, PHQ9, MAIA, STAIT, 
# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ 
# names(df8a)  # EDI, BPQ
# names(df8b)  # PHQ9, PHQ15, TAS
# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
# names(df10)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
# names(df11)  # PHQ4, STAIT5, BDI, MAIA
# names(df12) # MAIA, PI, 
# names(df14) # MAIA, TAS, MFQ(DEP), STAI(ANX)
# names(df15) #
# names(df16) #
